
---
title: "Website Analytics"
---

## Website Analytics Report

This page explains how website traffic data can be collected, connected, and analyzed using Google Analytics 4 and related tools.

## Connecting Website to Google Analytics

Google Analytics 4 can be connected to a website by adding the tracking tag to the site. This allows website traffic and user behavior data to be collected.

## Connecting Google Search Console to Google Analytics

Google Search Console can be linked to Google Analytics to better understand search performance, impressions, and organic traffic.

## Reading Google Analytics from Google BigQuery

Google Analytics data can be exported to BigQuery, where larger and more detailed analyses can be performed.

## Visualizing Data in Looker Studio

Looker Studio can be used to visualize traffic and conversion metrics such as:

- Users
- Sessions
- Traffic source
- Engagement
- Conversions

## Sample Traffic Visualization

```{r}
library(tidyverse)

traffic_data <- tibble(
  source = c("Direct", "Organic Search", "Social", "Referral"),
  users = c(420, 310, 260, 110)
)

ggplot(traffic_data, aes(x = source, y = users)) +
  geom_col() +
  labs(
    title = "Sample Website Users by Traffic Source",
    x = "Traffic Source",
    y = "Users"
  ) +
  theme_minimal()
```

## Sample Conversion

```{r}
conversion_data <- tibble(
  metric = c("Sessions", "Engaged Sessions", "Conversions"),
  value = c(1240, 860, 145)
)

ggplot(conversion_data, aes(x = metric, y = value)) +
  geom_col() +
  labs(
    title = "Sample Traffic and Conversion Metrics",
    x = "Metric",
    y = "Value"
  ) +
  theme_minimal()
```

## Insights
-   Direct traffic is the strongest source of users
-   Organic search and social media also drive meaningful traffic
-   Engaged sessions make up a large share of total sessions
-   Conversion metrics help evaluate website effectiveness

## Conclusion

> Website analytics helps identify which channels perform best, how users behave, and where marketing improvements can create stronger results.
