---
title: "Dashboard"
---

## Dashboard

This page presents sample visualizations similar to the kinds of dashboards used in marketing and social media reporting.

## Social Media Engagement by Platform

```{r}
library(tidyverse)

engagement_data <- tibble(
  platform = c("Instagram", "TikTok", "Facebook"),
  engagement = c(820, 1040, 430)
)

ggplot(engagement_data, aes(x = platform, y = engagement)) +
  geom_col() +
  labs(
    title = "Sample Social Media Engagement by Platform",
    x = "Platform",
    y = "Engagement"
  ) +
  theme_minimal()
```

## Audience Reach Over Time

```{r}
reach_data <- tibble(
  month = c("January", "February", "March", "April"),
  reach = c(1800, 2200, 2600, 3100)
)

ggplot(reach_data, aes(x = month, y = reach, group = 1)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Sample Audience Reach Over Time",
    x = "Month",
    y = "Reach"
  ) +
  theme_minimal()
```

## Dashboard Insights
-   Instagram and TikTok show higher engagement than Facebook
-   Audience reach increases over time
-   Dashboards make campaign performance easier to understand


